Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Wording of "Solution"

As we explained in Section~\ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two extensions to Haddock's markup.
And combinators for expectations, that can be used with Hspec, are
introduced.

@@

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
Examples and properties in Haddock comments are automatically
tested by the Doctest command.
Its implementation will be discussed in Section~\ref{sec:doctest}.

>>>>

As we explained in Section~\ref{sec:problem},
we use Doctest for user documentation and Hspec for code documentation.
The following subsections explain two extensions to Haddock's markup.
Subsequently, combinators for expectations, that can be used with
Hspec, are introduced.

@@

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item
    Implement a tool, similar to Python's Doctest, that can verify
    examples and test properties in Haddock comments.
    The implementation is discussed in Section~\ref{sec:doctest}.
